```{r}
require(dplyr)

```


```{r}
spark <- read.csv('Spark_rounds.csv')

head(spark)
```

```{r}
tail(spark)
```

```{r}
dim(spark)
```


```{r}
names(spark)
```


```{r}
colSums(is.na(spark))

```

```{r}
spark$company_permalink <- sapply(spark$company_permalink, toupper)
```




# count no of companies
```{r}
sum(!duplicated(spark$company_permalink))
```



# Average funding amount of venture type
# Average funding amount of angel type
# Average funding amount of seed type
# Average funding amount of private equity type
```{r}
summarise(group_by(spark,funding_round_type),Average = mean(raised_amount_usd, na.rm = T))


```



#Considering that Spark Funds wants to invest between 5 to 15 million USD per investment round, which investment type is the most suitable for them?
```{r}
summarise(group_by(spark,funding_round_type),Average = mean(raised_amount_usd, na.rm = T)) %>% 
  filter(Average > 5000000 & Average < 15000000)



```







# Companies Dataset
```{r}

companies_df <- read.csv("Spark_Companies.txt", sep = "\t")

head(companies_df)

```

```{r}
View(companies_df)

dim(companies_df)

```


```{r}
names(companies_df)
```


```{r}
colSums(companies_df == "")

```


# In the companies data frame, which column can be used as the unique key for each company? Write the name of the column.
```{r}
sum(duplicated(companies_df$permalink))
```
# Ans : permalink (There is no duplicate value)



```{r}
companies_df$permalink <- sapply(companies_df$permalink, toupper)
```


# How many unique companies are present in the companies file?
```{r}
sum(! duplicated(companies_df$permalink))

```


```{r}

master_frame <- merge(x = spark,y = companies_df, by.x = "company_permalink", by.y = "permalink")

head(master_frame)

```

```{r}

dim(master_frame)
```
# Read Countries Data

```{r}
countries_df <- read.csv("countries.csv")

head(countries_df)
```


```{r}
master_frame_1 <-  merge(x = master_frame, y = countries_df, by = "country_code", all.x = T)
```



```{r}
names(master_frame_1)
```



```{r}
contries_gb = summarise(group_by(master_frame_1,country_code,country,continent),raised_amount_usd = sum(raised_amount_usd, na.rm = T))
```
```{r}

View(contries_gb)

```

